Who Cares About Crackdowns? Exploring the Role of Trust in Individual Philanthropy

### 2021-04-22 manuscript/manuscript.Rmd
Change one (1) word

In this paper, we look at which kinds of donors are more or less likely to consider an NGO's issue area, funding sources, and relationships with host governments when deciding to donate. Disentangling the effect of every individual level-characteristic measured in the survey on every combination of organizational characteristics presented in the conjoint experiment is unwieldy and near impossible. For instance, we might posit that politically conservative, religiously active personas that have a history of charitable giving and high trust in nonprofits might be more likely to donate to disaster relief organizations facing government crackdown. But that is only one possible combination—given the organizational attributes presented in our experiment, and the possible individual characteristics that respondents could select, there are billions of possible iterations of organizational and individual attributes, many of which rarely occur in the actual population of potential donors.

>>>>

In this paper, we look at which kinds of donors are more or less likely to consider an NGO's issue area, funding sources, and relationships with host governments when deciding to donate. Disentangling the effect of every individual level-characteristic measured in the survey on every combination of organizational attribute presented in the conjoint experiment is unwieldy and near impossible. For instance, we might posit that politically conservative, religiously active personas that have a history of charitable giving and high trust in nonprofits might be more likely to donate to disaster relief organizations facing government crackdown. But that is only one possible combination—given the organizational attributes presented in our experiment, and the possible individual characteristics that respondents could select, there are billions of possible iterations of organizational and individual attributes, many of which rarely occur in the actual population of potential donors.
